\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-21 manuscript/main.tex
modified:   analysis/final_analysis.do 	modified:   analysis/individual.do 	modified:   cleaning/clean individual.do 	modified:   cleaning/merged_back_to_the_individual.ipynb 	modified:   manuscript/main.tex 	modified:   result_tables/entry_effect_hetero.tex 	modified:   result_tables/formulate_the_tables.ipynb

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DiD) estimation technique. The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing a unique natural experiment to examine the effects of offline expansion on the local real estate market. Although Lianjia's entry is not a randomized event, the DiD estimation method remains robust in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on any of the three outcomes, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider a unique exogenous shock that occurred during our study period. During our study period, Lianjia implemented the ACN strategy. ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store. For this purpose, Lianjia can cooperate with other competitors in the market and integrate their resources to provide a better service to the customers. This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:

>>>>

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DiD) estimation technique. The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing an unique natural experiment to examine the effects of offline expansion on the local real estate market. Although Lianjia's entry is not a randomized event, the DiD estimation method remains unbiased in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

@@

The result presented in the table \ref{tab:entry_effect} examines the effect of Lianjia's offline stores' entry into an area on various outcomes. Prior to the Lianjia's entry ($pre_2$), there is no statistically significant effect on Lianjia's transaction properties, suggesting that anticipation of the Lianjia's entry does not affect these metrics. In addition, there is a significant 4\% increase in revenue after the Lianjia's entry ($entry$), suggesting a substantial increase in Lianjia sales. However, the effect on price concessions and number of showings remains statistically insignificant, suggesting that Lianjia's entry does not lead to significant changes in pricing strategies or the number of showings brought to the area.

@@

To empirically estimate the effect of Lianjia's platform strategy, we consider an exogenous shock that occurred during our study period. During our study period, Lianjia implemented the ACN strategy. ACN means to subdivide the whole process of buying and selling a house into different parts, and each part is taken charge of by a person or a store. For this purpose, Lianjia can cooperate with other competitors in the market and integrate their resources to provide a better service to the customers. This strategy is a significant change in Lianjia's business model, and it is expected to have a significant impact on the market. In addition to this, Lianjia also opened up the form of franchises and gradually started platform integration. To empirically measure the effect of platformization to the offline stores' operations, we first counted the number of all non-Lianjia stores on the Lianjia's Beke platform within a radius of 410 meters, which allowed us to generate a dummy variable $Treatment_{it}$ to represent whether or not there are any other affiliate stores within the platform in this neighborhood. To dynamically capture the varying effects, we generate $Treatmetn_{it} * year$ by producting the year dummy variable with the $Treatment_{it}$ and include them in our regression model. Since the ACN network was officially established at the end of 2018, we can generate a dummy variable equal to 1 if the year is greater than 2018. We then consider the following regression model:
